---
title: "MATH 4322 Lab 2"
author: "Ayub Farah"
format: pdf
editor: visual
---

## Task 1

```{r}
library(ISLR2)
head(Boston)
```

### Question 1

For the 6th suburb of Boston what is the median house value and the average\
number of rooms per dwelling?

```{r}
Boston[6, "rm"]
Boston[6, "medv"]
```

## Task 2

```{r}
plot(Boston$rm,Boston$medv,xlab = "rm",ylab = "medv")
```

### Question 2

According to the plot what is the relationship between median value of\
homes and average number of rooms per dwelling?

The relationship is somewhat strong, somewhat linear.

## Task 3

### Question 3

Which observation has the largest average number of rooms per dwelling?\
What is the largest average number of rooms per dwelling?

```{r}
max_rm <- which.max(Boston$rm)
max_rm
Boston[max_rm, "rm"]
```

### Question 4

Which observation has the smallest average number of rooms per dwelling?\
What is the smallest average number of rooms per dwelling?

```{r}
min_rm <- which.min(Boston$rm)
min_rm
Boston[min_rm, "rm"]
```

## Task 4

```{r}
lm.fit <- lm(medv ~ rm, data = Boston)
summary(lm.fit)
```

### Question 5

Give the linear model equation.

$$
\hat{y} = 9.102x - 34.671
$$

where $\hat{y}$ is predicted `medv` and $x$ is `rm`.

### Question 6

What is the percent of variation of `medv`that can be explained by this model?

$$
48.35\%\
$$

### Question 7

Is rm a good predictor for `medv`? Justify your answer.

The $R^2$ for this model is fairly low, since it explains less than half the variation in observed `medv` .

## Task 5

### Question 8 

What is the 95% confidence interval for the slope $\beta_1$ of this model?

```{r}
confint.lm(lm.fit, level=0.9)
```

## Task 6

### Question 9

What is the predicted median value of homes where the average number of\
rooms per dwelling is 5?

```{r}
 (9.102*5) - 34.671
```

## Task 7

```{r}
par(mfrow = c(2,2))
plot(lm.fit)
```

### Question 10

Do there appear to be extreme values?

Yes.

### Question 11

Which row has the largest leverage?

```{r}
max_leverage <- which.max(hatvalues(lm.fit))
Boston[max_leverage, ]
```

### Question 12

How many average number of rooms per dwelling and what is the median\
value of the homes in this suburb?

```{r}
Boston[max_leverage, "rm"]
Boston[max_leverage, "medv"]
```
