---
title: "Homework 1 - MATH 4322"
author: "Ayub Farah"
format: pdf
editor: visual
---

## Problem 1

a\. This is a regression and inference problem, because we are making inferences about the factors that influence CEO salary, a continuous value. Our $n$ is 500 and $p$ is 3 (inputs: profit, number of employees, industry) + 1 (output: CEO salary).

b\. This is a classification and prediction problem, because we are predicting whether or not customers will default on their credit card, a categorical value. Our $n$ is 550 and $p$ is 3 (inputs: studentship, average balance after making monthly payment, income) + 1 (output: whether or not the customer defaulted).

## Problem 2

a\.

$$
E[\hat{\mu_1}] = E[X_1] = \mu, \ \text{Bias}(\mu_1) = E[\bar{\mu_1}] - \mu = 0 \\ 
E[\hat{\mu_2}] = E[0.1X_1 + 0.2X_2 + 0.3X_3 + 0.4X_4] = 0.1\mu + 0.2\mu + 0.3\mu + 0.4\mu = \mu, \ \text{Bias}(\mu_2) = E[\bar{\mu_2}] - \mu = 0 \\
E[\hat{\mu_3}] = \frac{1}{4} \sum^4_{i=1} X_i = \mu, \ \text{Bias}(\mu_3) = E[\bar{\mu_3}] - \mu = 0
$$

b\.

$$
\text{Var}[\hat{\mu_1}] = \text{Var}[X_1] = \sigma^2 \\ 
\text{Var}[\hat{\mu_2}] = \text{Var}[0.1X_1 + 0.2X_2 + 0.3X_3 + 0.4X_4] = (0.1)^2\text{Var}(X_1) + (0.2)^2\text{Var}(X_2) + (0.3)^2\text{Var}(X_3) + (0.4)^2\text{Var}(X_4) = 0.3\sigma^2 \\ 
\text{Var}[\hat{\mu_3}] = \text{Var}[\frac{1}{4} \sum^4_{i=1} X_i] = \frac{1}{8} \sum^4_{i=1} X_i = \frac{1}{2}\sigma^2
$$

c\. I would say $\hat{\mu_2}$ has the smallest variance at $0.3\sigma^2$.

## Problem 3

## Problem 4

```{r}
library(ISLR)
auto_ds <- na.omit(Auto)
auto_ds
```

a\.

Quantitative: mpg, cylinders, displacement, horsepower, weight, acceleration.

Qualitative: year, origin, name

b\.

mpg: 37.6, cylinders: 5, displacement: 387, horsepower: 184, weight: 3527, acceleration: 16.8

```{r}
summary(auto_ds)
```

c\.

Means:

mpg: 23.45, cylinders: 5.472, displacement: 194.4, horsepower: 104.5, weight: 2978, acceleration: 15.54

Std:

```{r}
for (x in list(auto_ds$mpg, auto_ds$cylinders, auto_ds$displacement, auto_ds$horsepower, auto_ds$weight, auto_ds$acceleration)) {
  print(sd(x))
}
```

d\.

```{r}
auto_removed <- auto_ds[-(10:85)]
summary(auto_removed)
```

```{r}
for (x in list(auto_removed$mpg, auto_removed$cylinders, auto_removed$displacement, auto_removed$horsepower, auto_removed$weight, auto_removed$acceleration)) {
  print(sd(x))
}
```

## Problem 5

a\.

```{r}
college <- read.csv("College.csv")
head(college)
```

b\.

```{r}
# rownames(college) <- college[,1]
# college <- college[,-1]
head(college)
```
